\input{settings.tex}

\usepackage{times}

\begin{document}
\begin{center}
\Large{\textbf{Julián Ceballos}}
\linebreak
\small{\textbf{Current:} Estocolmo \# 23 X Paseo de Reforma, Ciudad de México.}
\linebreak
\href{http://about.me/jceb}{\underline{http://about.me/jceb}}
\end{center}
\colorbox{black}{\makebox[\textwidth][l]{\color{white}{\textbf{Aim}}}}
\linebreak
\makebox[\textwidth][l]{\color{black}{Innovate, build, promote and teach about technology innovation.}}
\linebreak
\makebox[\textwidth][l]{\color{black}{Programming is not a hobbie or job, is a life style.}}
\linebreak
\linebreak
\colorbox{black}{\makebox[\textwidth][l]{\color{white}{\textbf{Last Conferences and another}}}}
\linebreak
\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}} p{10cm} p{6.5cm} }
  \textbf{Open web development} & \textbf{SIECC 2011} \\
  \textit{Speaker} & \textit{Noviembre, 2011.} \\
  & \textit{Durango.} \\
  & \\
  \textbf{Mozilla México} & \textbf{Mozilla Summit 2010} \\
  \textit{Speaker} & \textit{July 6th, 2010} \\
  & \textit{Whistler, B.C., Canada} \\
\end{tabularx}
\linebreak
\linebreak
\linebreak
\colorbox{black}{\makebox[\textwidth][l]{\color{white}{\textbf{Last Professional expirience}}}}
\linebreak
\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}} p{10cm} p{6.5cm} }
  \textbf{Llorsat} & \textbf{México city} \\
  \textit{Senior developer} & \textit{March 2012 - Currently} \\
  Development of an ERP completely in Javascript, compatible with HTML5 standars, currently we are using Backbone, Handlebars, jQuery and a lot of other Javascript libraries to build our product and at same time we're building a kind of framework to make much faster the development. & \\
  & \\
  \textbf{Noster} & \textbf{Mérida, Yuc.} \\
  \textit{CTO} & \textit{December, 2010 - March, 2012} \\
  I was CTO in this company, building the iphone app, api and webapp of this product, we went to USA to ask for funding.  I deployed new features on daily basis to support customers needs. The technologies I was using was Apple iOS SDK, Django, Piston, Postgresql, Javascript, HTML5 and CSS3. This project concluded after two years of hard work.& \\
  & \\
  \textbf{Mozilla México} & \textbf{México} \\
  \textit{Development area leader} & \textit{March, 2008 - Actually} \\
  In Mozilla I was open web evangelist and developer for Mozilla's labs department. I didn’t receive an actual payment for my contributions here, but I loved this project because it was my first international project where I got the chance to do code contributions in Python - a language I love. I developed extensions in both Python and Javascrip for Firefox's Addon SDK, to enhance user expirience and tools. & \\
  & \\
  \textbf{ASI} & \textbf{Mérida, Yuc.} \\
  \textit{Junior developer} & \textit{May, 2010 - August, 2010} \\
  My first job in site, developing Geolocalization and tasks automatization applications for a company based on energy safe programs, in this company I was developing in Python for server side and just a few frontend-backend projects. & \\
  & \\
\end{tabularx}
\linebreak
\linebreak
\linebreak
\linebreak
\linebreak
\colorbox{black}{\makebox[\textwidth][l]{\color{white}{\textbf{Aditional information}}}}
\linebreak
\begin{tabularx}{\textwidth}{@{\extracolsep{\fill}} p{16.5cm} }
  \textbf{Languages:} Spanish(native), English. \\
  \textbf{Computing topics:} Python, Javascript, PHP, Objective C, C, C++, Coldfusion, Ruby on rails, Django, Backbone, Handlebars, jQuery, bottlepy, SQLite, MySQL, Mongodb, Windows, Linux, Macos. \\
  \textbf{Activities:} Learn by myself, soccer, go to cinema, develop my system ideas, collaborate in other projects. \\
  \textbf{Another knowledges:} Git, Hg, Scrum, Lean startup, MVP development, Kanban. \\
\end{tabularx}
\end{document}
